\documentclass[12pt]{report}
\setcounter{tocdepth}{2}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\graphicspath{ {images/} }

\usepackage[a4paper,width=150mm,top=25mm,bottom=25mm]{geometry}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead[RO]{\thechapter}

\usepackage{caption}
\usepackage{subcaption}

\usepackage[backend=biber]{biblatex} 
\addbibresource{references.bib}

\usepackage{setspace}
\doublespacing

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bbm}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\usepackage{indentfirst}

\usepackage{siunitx}
\usepackage{textcomp}

% For quotes
\usepackage{framed}

% Table label on top
\usepackage{float}
\floatstyle{plaintop}
\restylefloat{table}

% Foot notes
\newcommand\blfootnote[1]{%
  \begingroup
  \renewcommand\thefootnote{}\footnote{#1}%
  \addtocounter{footnote}{-1}%
  \endgroup
}

% Optimization
\usepackage{optidef}

% For multi row tables
\usepackage{multirow}

% Color text
\usepackage{xcolor}

% For appendix
\usepackage[toc]{appendix}

% For wrapping text
\newcolumntype{L}{>{\centering\arraybackslash}m{4.5cm}}
\newcolumntype{C}[1]{>{\arraybackslash}p{#1}}

% For pseudo code for WWTP
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%% Begin Title Page %%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{titlepage}
    \begin{center}
    
        \vspace*{1.1cm}
        
        \LARGE
        Adaptive Control: A Study of Online Learning Optimal Control and Optimization Methods for Industrial Processes \\
        
        \vspace{1cm}
        
        \normalsize by \\
        
        \vspace{1cm}
        
        \large Rui Nian \\
        
        \vspace{3cm}
        
        {\normalsize
        A thesis submitted in partial fulfillment of the requirements for the degree of \\
        \vspace{1cm}}
        Master of Science \\
        {\normalsize in} \\ 
        Computer Process Control \\
        
        \vspace{3cm}
        
        {\normalsize
        Department of Chemical and Materials Engineering \\
        University of Alberta \\}
        
        \vspace{1cm}
        
        {\normalsize
        \textcopyright \hspace{1mm} Rui Nian, 2019 \\}
        

    \end{center}
\end{titlepage}
%%%%%%%%%%%%%%%%%%%%%%% End Title Page %%%%%%%%%%%%%%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%%%%%%%%%% Begin Main Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagenumbering{roman}
\setcounter{page}{2}
\chapter*{Abstract}

\chapter*{Preface}
This thesis is an original work by Rui Nian. Some of the research conducted was an collaborative effort between different organizations.  For Chapters 2 and 3, the machine learning project was partially funded by Mitacs through the Mitacs Accelerate Program.  Additionally, the project was a joint effort between the University of Alberta, an unnamed large energy company \footnote{The company management team preferred to stay anonymous within this thesis, and would like to be referred to as "an unnamed large energy company".}, Willowglen Systems Inc., and Alberta Machine Intelligence Institute (AMII). While all the algorithms were developed by myself, the unnamed large energy company and Willowglen's management team provided feedback regarding the complexity and accuracy of the algorithms desired. Additionally, AMII provided the optimization packages and code used in the optimization portions of the product. As of the completion of this thesis, the original tool was cloned onto a second project for similar optimization purposes; thus, the developed optimization toolbox is now applied onto two separate industrial pipelines. In Chapter 4, the waste water treatment plant and alarm management projects were conducted in collaboration with NTwist, a start-up AI company based in Edmonton, Alberta. Here, all algorithms were also developed by myself, but NTwist provided weekly feedback regarding what is feasible and infeasible in industry. Also in Chapter 4, the fault-tolerant control system project was completed in collaboration with Imperial Oil. The work here was also completed by myself, but the original research topic was provided by Imperial Oil. 

Parts of Chapter 1, 2, and 5 of this thesis was submitted as R. Nian, J. Liu, and B. Huang, \textit{"A Review and Tutorial on Reinforcement Learning: Introduction and Applications in Industrial Process Control", Processes}.  I obtained layout suggestions from my supervisors, Dr. Liu and Dr. Huang.  The manuscript was written by myself. The alarm management section in Chapter 3 was presented at the INFORMS Data Mining conference as R. Nian, J. Liu, B. Huang, and C. Meenavilli, \textit{"An Adaptive Alarm Prioritization, Reduction, and Optimization Algorithm for Enhanced Process Safety", INFORMS 2019}.  Additionally, the fault-tolerant control work was published in \textit{SICE 2019} by R. Nian, J. Liu, B. Huang, and T. Mutasa titled \textit{"Fault-tolerant Control System: A Reinforcement Learning Approach"}.

\tableofcontents
\listoffigures
\listoftables

\chapter*{Acknowledgements}
All the material presented in this thesis certainly could not have been achieved without the countless hours of undivided attention and focused guidance from my professors, colleagues, family and the online machine learning community. First of all, I would like to thank Dr. Fadi Ibrahim and Dr. VInay Prasad, the former being my previous co-op supervisor and the latter being a great mentor during my undergraduate studies, for being the catalyst which ultimately led me down the graduate studies path and introduced me to Dr. Biao Huang and Dr. Jinfeng Liu. Without Dr. Ibrahim and Dr. Prasad, I certainly would never have considered graduate school and would never have had the opportunity to learn as much as I have in the past two years.  

Next, I would like to gratefully thank both Dr. Jinfeng Liu and Dr. Biao Huang for the opportunity of pursuing my graduate studies here at the University of Alberta.  None of this work could have ever been possible without your continued trust, guidance, and never-ending support.  The learning opportunity was also greatly enhanced due to the vast amount of industrial sponsors that both Dr. Huang and Dr. Liu had due to their cutting edge research.  Additionally, the presentation experience I have obtained through to the weekly meetings and the IRC meetings are genuinely priceless.

And of course I cannot forget about my research groups for all the continued guidance and patience, accompanying me along my two year journey.  They are Ranjith Chiplunkar, Su Liu, Benjamin Nelson, Xunyuan Yin, Soumya Sahoo, Song Bo, An Zhang, and all other lab members who I did not get a chance to work with directly, but were definitely there to provide me with incredible feedback.  Without Ranjith's mathematical expertise, I would never have been able to understand many derivations and other highly theoretical topics.  Su helped me tremendously by providing initial recommendations to kick-start my first industrial project.  For coding help or theory regarding model predictive control, there was nobody better than Ben, who was always open to helping in any task. The waste water treatment plant project would have been impossible without Xunyuan and An's initial input and help on the model and other performance related topics.  And finally, Song was always available when I had very simple questions or simply wanted to chat!  Everyone was definitely a critical piece for my overall success.  

Another critical part that made my experience as a graduate student much more complete was the chance to work directly with large industrial sponsors through NTwist and Mitacs.  Here, I would like to express my thanks to Chowdary Meenavilli, NTwist, and Mitacs.  Because of them, I had the opportunity to work directly on real industrial issues and formulating innovative new ways to solve them.

Additionally, I would like to extend a warm appreciation to Professor John Cocchio and Dr. Lisa White, and Dr. Xunyuan Yin for allowing me to be the teaching assistant for ENGG 404 and Ch E 358, respectively.  Being a teaching assistant allowed me to see the other side of the table; the hardships and difficulty in teaching courses fairly and effectively.

But not all collaborators helped me in the technical aspect.  Some of my most critical collaborators supported me emotionally and provided for my social needs.  These individuals are, of course, my mom and dad, Ling Yan Gai, Hong Hui Nian.  My grandpa, Dou Shu Gai, my younger brother, Sunny Nian, and my girlfriend, Vivian Tran.  Without them, my mental aptitude would not have been resilient enough to allow me to push towards my limits.

And finally, to the unsung heroes of the machine learning community.  I would like to express my sincerest gratitude for spending so much time in crafting \textit{excellent} free, and easy to understand content so aspiring machine learning practitioners can learn the basics without running into a wall of technical jargon.  These materials posted online truly serve as a gateway to a new, untapped world. A special thanks goes out to Dr. Andrew Ng and his team for starting Coursera, an economically-smart and value-heavy online course platform. In the future, I will take the community's guidance and pass it forward to the next generation of upcoming machine learning engineers and data scientists.

\chapter*{Nomenclature}
\noindent 
\begin{tabular}{@{}ll}
ADAM & Adaptive momentum gradient descent \\
ADASYN & Adaptive Synthetic \\
ADP & Approximate dynamic programming \\
AI & Artificial intelligence \\
BGD & Batch gradient descent \\
CMDP & Constrained Markov decision process \\
CSTR & Continuously stirred tank reactor \\
DDPG & Deep deterministic policy gradient \\
DPG & Deterministic policy gradient \\
DP & Dynamic programming \\
DQN & Deep $Q$-learning network \\
FOMDP & Fully observable Markov decision process \\
FTC & Fault tolerant control \\
GAN & Generative Adversarial Networks \\
HVAC & Heating, ventilation, air conditioning \\
LPV & Linear parameter-varying \\
MAE & Mean absolute error \\
MC & Monte Carlo \\
MDP & Markov decision process \\
MIMO & Multiple-input multiple-output \\
MRP & Markov reward process
\end{tabular}

\newpage
\begin{tabular}{@{}ll}
ML & Machine learning \\
MP & Mathematical programming \\
MPC & Model predictive control \\
MSE & Mean squared error \\
NP & Non-deterministic polynomial time \\
OU & Ornstein-Uhlenbeck \\
PDP & Partial dependence plot \\
PID & Proportional Integral Derivative controller \\
POMDP & Partially observable Markov decision process \\
RL & Reinforcement learning \\
RNN & Recurrent neural network \\
RTO & Real time optimization \\
SGD & Stochastic gradient descent \\
SISO & Single-input single-output \\
SMDP & Semi Markov decision process \\
SMOTE & Synthetic Minority Over-sampling Technique \\
sp & Set-point \\
ss & Steady state \\
TD & Temporal difference \\
TITO & Two-input two-output \\
UCB & Upper confidence bound \\
VFD & Variable frequency drive \\
WWTP & Waste water treatment plant \\
\end{tabular}

% \chapter{Introduction}
\pagenumbering{arabic}
% \input{chapters/Chapter01:Introduction.tex}

% \chapter{Machine Learning for Prediction Applications}
% \input{chapters/Chapter02:MachineLearningforPrediction.tex}

% \chapter{Machine Learning for Process Monitoring}
% \input{chapters/Chapter03:MachineLearningforMonitoring.tex}

\chapter{Machine Learning for Control Applications}
\input{chapters/Chapter04:MachineLearningforControl.tex}

% \chapter{Review of RL for Process Control}
% \input{chapters/Chapter05:ProcessControlRL.tex}

% \chapter{Concluding Remarks}
% \input{chapters/Chapter06:Conclusion.tex}

\printbibliography

\appendix

% Only one for sure in appendix
% \chapter{Process Monitoring and Optimization of an Industrial Pipeline}
% \input{chapters/AppendixA:Suncor.tex}

% % Might include in body
% \chapter{Distillation Tower Fault Prevention using Reinforcement Learning}
% \input{chapters/AppendixB:ImperialOilProject.tex}

% % Might include in body
% \chapter{Optimal Control and Alarm Management of a Waste Water Treatment Process}
% \input{chapters/AppendixC:WWTP.tex}

\end{document}
